Forecasting the 2024 US General Election

### 2024-11-04 paper/paper.qmd
more refinement on the data section

### Sample Size
The sample size of a poll is the number of people who participated in the poll. Generally, a larger sample size is seen as a better representation of the population. The most common sample size of polls is around 1250, as seen in @fig-sample-size.

>>>>

### Sample Size
The sample size of a poll refers to the number of individuals who participated in the poll. Generally, a larger sample size is considered to provide a more accurate representation of the overall population. For instance, a common sample size for polls is greater than 1000. While this might seem like a relatively small number, studies have shown that sample sizes exceeding 1,004 can achieve a margin of error less than 3 percent,  @citeScientificAmerican. Sample sizes in our dataset have a mode of 1250, as seen in @fig-sample-size, which suggests that most of the polls in the dataset adhere to accepted polling practices when it comes to sample size.
